\newif\iftechnical\technicaltrue

%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{blue}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex or lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean


\usepackage{fontawesome5}  % for extra icons
\usepackage{enumitem}  % manage spacing for enum

% adjust the page margins
\usepackage[scale=0.8]{geometry}
% \usepackage{titlesec}                            % used to change the section spacing
% \setlength{\hintscolumnwidth}{2.25cm}              % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Cheng}{Zhang}
\title{Curriculum vitae}
\email{czhang03@bu.edu}                               % optional, remove / comment the line if not wanted
\homepage{cs-people.bu.edu/czhang03/}              % optional, remove / comment the line if not wanted
\social[github]{chantisnake}                              % optional, remove / comment the line if not wanted
\extrainfo{\faFile{}~\href{https://cdn.jsdelivr.net/gh/chantisnake/CV@master/main.pdf}{curriculum vitae}}


% bibliography adjustments (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}

% bibliography with multiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       --------------------------------------------------------

% Display the CV title
\makecvtitle{}

% set the space between \cventry
\setlength{\parskip}{2.5px}
\linespread{1.3}
\selectfont


\section{Education}

\cventry{2018 --- Now}
{Computer Science, \iftechnical Doctor of Philosophy\else Ph.D.\fi} {}
{Boston University}
{Boston, MA}
{\textbf{Primary Interest}: Algebra Method for Program Verification\\
\iftechnical
I am broadly interested in application of mathematics in computer science,
especially in programming languages.
I have worked on Kleene algebra, program logics, semantics, type systems, and category theories.
\else 
I have worked on static analysis, type systems, and software engineering principles.
\fi}  % description

\cventry{2022}
{Oregon Programming Language Summer School (OPLSS)}{}
{University of Oregon}{Eugene, OR}
{
\iftechnical
\else   
This year, the school focused on Types, Semantics, and Program Reasoning;
\fi
I have attended courses involving proof theory,
type theory, algebraic effect system, program verification in Coq etc.}


\cventry{2021}
{Oregon Programming Language Summer School (OPLSS)}{}
{University of Oregon}{Eugene, OR}
{
\iftechnical
\else   
This year, the school focused on foundation of programming and security;
\fi
I have attended courses involving verification of probabilistic programs,
session type for concurrent programming, 
and categorical semantics of advanced type systems, etc.}


\cventry{2014 --- 2018}
{Mathematics, \iftechnical Bachelor of Art\else B.A.\fi} {with department honor, magna cum laude}
{Wheaton College}
{Norton, MA}
{\textbf{Honor Thesis}: \href{http://hdl.handle.net/11040/24570}{King in Generalized Tournaments}.\\
\textbf{Minors}: Computer Science, Economics.
}

\cventry{2016 --- 2017}
{Economics, Study Aboard} {}
{London School Of Economics}
{London, United Kingdom}
{}  % description



\section{Publications And Preprints}

\cventry{2022}
{Cheng Zhang, Arthur Azevedo de Amorim, Marco Gaboardi}
{\href{https://arxiv.org/abs/2108.07707}{On Incorrectness Logic and Kleene Algebra With Top and Tests}}
{Principle Of Programming Language (POPL)}
{}{}

\cventry{2020}
{Mark Lemay, Cheng Zhang, William Blair}
{\href{https://icfp20.sigplan.org/details/tyde-2020-papers/7/Developing-a-Dependently-Typed-Language-with-Runtime-Proof-Search-Extended-Abstract-}
{Developing a Dependently Typed Language with Runtime Proof Search (Extended Abstract)}}
{Workshop on Type-Driven Development (TyDe)}
{}{}

\cventry{2018}
{Cheng Zhang}
{\href{http://hdl.handle.net/11040/24570}{King in Generalized Tournaments}}
{Wheaton College Honor Thesis}
{}{}

\cventry{2018}
{Cheng Zhang, Weiqi Feng, Emma Steffens, Alvaro de Landaluce, Scott Kleinman, Mark D. LeBlanc}
{\href{https://dl.acm.org/doi/10.5555/3205191.3205205}{Lexos 2017: Building Reliable Software in Python}}
{Journal of Computing Sciences in Colleges}
{}{}


\section{Research Talks}

\cventry{2022}
{Cheng Zhang}
{Kleene Algebra and Its Applications in Verification}
{Boston Computation Club}
{}{}

\cventry{2022}
{Cheng Zhang}
{On Incorrectness Logic Kleene Algebra With Test}
{Cornell Programming Language Discussion Group (PLDG)}
{}{}

\cventry{2022}
{Cheng Zhang}
{On Incorrectness Logic Kleene Algebra With Test}
{Principle Of Programming Languages (POPL)}
{}{}

\cventry{2018}
{Cheng Zhang, Mark D. LeBlanc}
{Lexos 2017: Building Reliable Software in Python}
{Journal of Computing Sciences in Colleges}
{}{}

\cventry{2018}
{Cheng Zhang}
{Kings in Quasi-transitive Oriented Graph}
{Wheaton Summit For Woman In STEM}
{}{}


\section{Research Projects}

\cventry{2021 --- Now}
{Probabilistic Incorrectness Logic}
{Boston University}{Boston, MA}{}
{Examine the mathematical foundation of probabilistic Incorrectness logic.
This work \iftechnical may \else will \fi 
give rise to a method to identify the probability of encountering bugs in programs.}

\cventry{2020 --- 2022}
{Algebraic Formulation Of Incorrectness Logic}
{Boston University}{Boston, MA}{}
{Provide a algebraic formulation of Incorrectness Logic in TopKAT.
Our work leads to simpler proofs for program incorrectness, 
and demonstrates ways to automatically certify bugs in programs.
\iftechnical
We showed that 
TopKAT is a minimal framework to model incorrectness,
as it is impossible to encode incorrectness logic in KAT.
After that, we proved many meta-theoretical property of TopKAT,
including incompleteness with relational model, 
completeness of general relational model and language model, 
complexity of deciding equality, and expressivity of general relational model.
\else 
We have also showed that 
TopKAT is a minimal framework to model incorrectness,
as it is impossible to encode incorrectness logic in KAT.
\fi
}

\cventry{2017 --- 2018}
{Mathematics Honor Thesis}
{Wheaton College} {Norton, MA}{}
{Studied kings in generalizations of tournament,
with a special focus on quasi-transitive oriented graphs.
I have shown that all the quasi-transitive oriented graphs
can be condensed into a tournament via tie component condensation, 
and tie component condensation of quasi-transitive 
oriented graphs is the most efficient condensation to tournament.
}

\cventry{2015 --- 2018}
{Software Lead}
{Lexomics Research Group, Wheaton College}
{Norton, MA}{}
{
  Led a group of undergraduate engineers through a major factorization of 
  the natrual language processing (NLP) software 
  \href{https://github.com/WheatonCS/Lexos}{Lexos}.
  In the process, 
  I have designed a new architecture for side-effect management,
  transitioned the code base to a scalable functional-first paradigm,
  implemented industry-standard software development workflows,
  and provided detailed documentations and guides for the entire system.
}


\section{Honors And Fellowships}
\cvitem{2022}{Meta PhD Research Fellowship Finalist in Programminag Languages}
\cvitem{2018 --- Now} {Phi Beta Kappa Honor Society Member.}
\cvitem{2018}{Boston University Dean's Fellowship.}
\cvitem{2018}{Phi Beta Kappa Graduate Scholarship.}
\cvitem{2018} {Madeleine F. Clark Wallace Mathematics Prize.}
\cvitem{2018}{Fred Kollett Prize in Mathematics \& Computer Science.}
\cvitem{2017}{Weaton College Faculty-Student Research Awards.}
\cvitem{2016}{Wheaton Fellows.}
\cvitem{2014 --- 2018}{Wheaton College International Scholarship.}
\cvitem{2014 --- 2018}{Wheaton College Dean's Lists.}


\section{Technical Skills}

\iftechnical
\cvline{}{\textbf{Programming}: Haskell, ATS, Python, TypeScript.}
\cvline{}{\textbf{Formal Methods}: Coq, MathComp, Z3.}
\cvline{}{\textbf{Data Processing}: Panda, Scikit-Learn, Numpy, R.}
\cvitem{}{\textbf{Tools}: Git, \LaTeX, SSH, Jupyter Notebook.}
\else
\cvline{}{\textbf{Programming Languages}: Haskell, Ocaml, ATS, TypeScript, C\#, Java, C++.}
\cvline{}{\textbf{Scripting Languages}: Python, Powershell, JavaScript, Mathematica.}
\cvline{}{\textbf{Formal Methods}: Coq, Lean, MathComp Z3, EasyCrypt, Agda.}
\cvline{}{\textbf{Data Processing}: Panda, Scikit-Learn, Numpy, SQL, R, Stata.}
\cvitem{}{\textbf{Tools}: Git, \LaTeX, SSH, Jupyter Notebook.}
\fi


\section{Professional Experiences}

\cventry{2019 --- Now}
{Graduate Researcher}
{Boston University}
{Boston, MA}{}
{Study various extensions of Kleene Algebra, and their use in program analysis
of imperative/functional programs, probabilistic programs, distributed systems, networks, etc.
My researches provide easier, even automated, proofs for program analysis.
}

\cventry{2019 --- 2021}
{Teaching Fellow}
{Boston University}
{Boston, MA}{}
{
  Taught Principle of Programming Language, Introduction to Computer Science,
  Algebra Algorithm, Geometric Algorithm, etc.
}


\cventry{2021 --- Now}
{Organizer}
{Principle of Programming and Verification Seminar}
{Boston University}{Boston, MA}
{Invite seminar speakers and coordinate time of the talks;
maintain seminar webpage, mailing list, and calendar;
distribute details of the seminar to participants every week;
and host speakers during the seminars.}

\cventry{2020 --- Now}
{Organizer}
{Programming Language Reading Group}
{Boston University}{Boston, MA}
{Identify and distribute weekly reading materials;
host and schedule the weekly discussions.}

\cventry{2019}
{Grader}
{Boston University CS 511 Formal Method}
{Boston, MA}{}
{Provided solutions to homework problems, graded the homework,
organize useful statistics for the professor, 
and provided hints and answered questions piazza when necessary.}

\cventry{2017 --- 2018}
{Grader}
{Wheaton College MATH 241 Theory of Probability}
{Norton, MA}{}
{Graded homework, gave feedback to students on each individual homework,
and provide informative statistics to the professor on the homework.}


\section{Selected Coursework}

\cventry{2018 --- Now}
{Computer Science, \iftechnical Doctor of Philosophy\else Ph.D.\fi} {}
{Boston University} {} {}  % description
\cvlistdoubleitem{Computer Network}{Cryptography}
\cvlistdoubleitem{Formal Method}{Compilers}
\cvlistdoubleitem{Overview On Type Systems}{Complexity Thoery}


\cventry{2014 --- 2018}
{Mathematics, \iftechnical Bachelor of Art\else B.A.\fi} {}
{Wheaton College} {} {}
\cvlistdoubleitem{Complex Analysis}{Real Analysis}
\cvlistdoubleitem{Graph Thoery}{Theory Of Computation}
\cvlistdoubleitem{Mathematical Statistics}{Advanced Cryptography}

\cventry{2016 --- 2017}
{Economics, Study Aboard} {}
{London School Of Economics} {} {}  % description
\cvlistdoubleitem{Game Thoery}{Economatrics}
\cvlistdoubleitem{Abstract Algebra I}{Abstract Algebra II}


\end{document}
