
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% resume - one page, one column
% XeLaTeX Template
% Version 1.1 (09.05.2017)
%
% Author: knyte (https://github.com/knyte)
%
% Repository: https://github.com/knyte/resume
%
% This template is primarily designed for
% undergraduate EE/CE/CS students applying for
% industry roles in software engineering
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{resume-knyte}
\usepackage{hyperref}

\begin{document}

%%%%%%%%%
% HEADER
%%%%%%%%%

% \makeheader{title/name}
\makeheader{Cheng Zhang}

%%%%%%%%%%%%
% SUBHEADER
%%%%%%%%%%%%

% argument to environment should match number of sites
\begin{subheader}{1}
% leave third argument empty to specify no hyperlink
    \site{GitHub}{Chantisnake}{https://github.com/chantisnake}
    \site{Email}{zcsx.ok at outlook dot com}{mailto://zcsx.ok@outlook.com}
    \site{Phone}{(+1)508-818-8290}{}\\

\end{subheader}

%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%
\begin{topic}{Education}

    % \entry{institution}{dates}{subtitle}{description}

    \entry{Wheaton College, Norton, MA}{Sep. 2014 - Present}
    {Candidate for Bachelor of Art, Expected May 2018}
    {Major in Mathematics, Minor in Computer Science and Economics.\\
     Major GPA: 3.9, General GPA: 3.84.\\
    Honors: Dean's List (for all the 4 semesters), Wheaton Fellow, Faculty Student Grant.}


    \entry{London School Of Economics, London, England}{Sep. 2016 - Jun. 2017}
    {Study Aboard}
    {Completed course work: Principles of Econometrics, Microeconomic Principles II, Game Theory,
     Algebra and Number Theory, Algebra and its Applications.
    }

    \\ % hard coded to adjust spacing
\end{topic}


%%%%%%%%%%%
% Publications
%%%%%%%%%%%
\begin{topic}{Publications}

    % \publication{Author}{Notice}{Title}{Conference}

    \publication{Zhang, C., LeBlanc, M. D., Kleinman, S., Feng, W., Steffens, E., Landaluce, d. A.,}
    {(in peer review)}
    {``Lexos 2017: Building Reliable Software in Python''}
    {CCSCNE 2018 – Conference for Computing in Small Colleges, UNH-Manchester, April 2018}

    \\
\end{topic}


%%%%%%%%%
% SKILLS
%%%%%%%%%
\begin{topic}{Skills}

    % \skillset{category}{members}

    \skillset{Programming Languages}
    {Experienced in Python and Powershell.\\
    Familiar with Haskell, F\#, Coq, TypeScript, JavaScript and \LaTeX{}.\\
    Basic idris, Scala, Elm, C\#, C++ and Java.}

    \skillset{Languages}
    {Fluent in English, Native Speaker in Chinese.}

    \\ % hardcoded due to entry spacing
\end{topic}


%%%%%%%%%%%%%
% EXPERIENCE
%%%%%%%%%%%%%
\begin{topic}{Experiences}

    % \entry{role}{dates}{team/company}{description}

    \entry{Mathematics Honor Thesis}{Sep. 2017 - Present}
    {Wheaton College Mathematics Department, Norton, MA}
    {Research on graph tournament, inspired by \href{https://www.maa.org/sites/default/files/pdf/upload_library/22/Allendoerfer/1981/0025570x.di021114.02p00982.pdf}{King Chicken Theorem}.
    My research focus on the kings behavior in improper tournaments (tournaments with ties).}

    \entry{Software Leader}{Jun. 2015 - Present}
    {Lexomics Research Group, Wheaton College, Norton, MA}
    {- Lead the development of \href{https://github.com/WheatonCS/Lexos}{Lexos}, a web app for text analysis workflow.\\
    - Help the team to adopt modern software development paradigm and workflow.\\
    - Designed a new architecture and a new python style guide for the project.}

    \entry{Open-source Contributor}{Sep. 2014 - Present}
    {Contributor to Many Open Source Projects}
    {Core developer of \href{https://github.com/janikvonrotz/awesome-powershell}{Awesome-Powershell}, \href{https://github.com/pcgeek86/PSGitHub}{PSGitHub}.
    Contribute Ideas to \href{https://github.com/python/typing}{python/typing}, \href{https://github.com/python/mypy}{mypy} and \href{https://github.com/siegebell/vscoq}{VSCoq}.
    Help to provide Minor improvement to \href{https://github.com/FStarLang/FStar}{FStar} and many other Projects.}

    \entry{Independent Mathematics Research}{Jun. 2016 - Jul. 2016}
    {Wheaton College Mathematics Department, Norton, MA}
    {Work with \href{https://wheatoncollege.edu/academics/faculty-directory/rochelle-shelly-leibowitz/}{Prof. Leibowitz}
    on the topic of \href{https://chantisnake.github.io/2016/05/22/explain-the-divisibility-graph/}{Divisibility Graph}.
    Found a way to construct prime divisibility graph directly, and a way to construct divisibility graph based on its factors.}

\\ % add spacing
\end{topic}

\newpage

%%%%%%%%%%%
% PROJECTS
%%%%%%%%%%%
\begin{topic}{Projects}

    % \entry{name}{dates}{summary}{description}

    \entry{PythonZ}{Sep. 2017 - Present}
    {Functional Programming In Python}
    {Project still in development.
    This project aims to showcase python's new type system, and implement typed functional feature in python.}

    \entry{Markdown for Academia}{Mar. 2017 - Apr. 2017}
    {An easy to use markup language designed for academic writing}
    {Semitics based on pandoc markdown, added many more feature to support academic writing.\\
    Can be compiled easily to HTML, PDF, \LaTeX{} and many other formats.}
    \\

\end{topic}

%%%%%%%%%%%
% EMPLOYMENT
%%%%%%%%%%%

\begin{topic}{Employment}
    \entry{Student Technician}{Sep 2015 - Present}
    {Second Level Technical Position working in the ITSS Help Desk}
    {First line of communication with end users.
    High level of Customer Service is a major part of this position.
    Experienced with computer hardware and software.}

    \entry{Math CS Grader}{Sep 2017 - Present}
    {Grader for Theory of Probability}
    {Grade the homework on theory of probability,
    and send the data analysis (grade distribution and error reason distribution)
    of the homework back to the professor every week.}
\end{topic}




\end{document}

