%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{blue}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex or lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean


\usepackage{fontawesome}  % for extra icons
\usepackage{enumitem}  % manage spacing for enum

% adjust the page margins
\usepackage[scale=0.8]{geometry}
% \usepackage{titlesec}                            % used to change the section spacing
\setlength{\hintscolumnwidth}{2.25cm}              % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Cheng}{Zhang}
\title{Résumé For 2022 Internship}
\email{czhang03@bu.edu}                               % optional, remove / comment the line if not wanted
\homepage{cs-people.bu.edu/czhang03/}              % optional, remove / comment the line if not wanted
\social[github]{chantisnake}                              % optional, remove / comment the line if not wanted
\extrainfo{\faFile{}~\href{https://cdn.jsdelivr.net/gh/chantisnake/CV@master/main.pdf}{Full CV}}


% bibliography adjustments (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}

% bibliography with multiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       --------------------------------------------------------

% Display the CV title
\makecvtitle{}

% set the space between \cventry
\setlength{\parskip}{2.5px}
\linespread{1.3}
\selectfont


\section{Education}

\cventry{2018 --- Now}
{Computer Science, Ph.D.} {}
{Boston University}
{Boston, MA}
{\textbf{Primary Interest}: Algebra Method in Program Analysis\\
I have also worked on program analysis, type systems,
and many intersections between computer science and mathematics.}  % description

\cventry{2014 --- 2018}
{Mathematics, B.A.} {with department honor, magna cum laude}
{Wheaton College}
{Norton, MA}
{\textbf{Honor Thesis}: \href{http://hdl.handle.net/11040/24570}{King in Generalized Tournaments}.\\
\textbf{Minors}: Computer Science, Economics.
}

\cventry{2016 --- 2017}
{Economics, Study Aboard} {}
{London School Of Economics}
{London, United Kingdom}
{}  % description



\section{Publications And Preprints}


\cventry{2022}
{Mark Lemay, Qiancheng Fu, Cheng Zhang, William Blair, Hongwei Xi}
{Gradual Correctness: a Dependently Typed Language with Dynamic Equality}
{Submitted to Certified Programs and Proofs (CPP)}{}{}

\cventry{2022}
{Cheng Zhang, Arthur Azevedo de Amorim, Marco Gaboardi}
{\href{https://arxiv.org/abs/2108.07707}{On Incorrectness Logic and Kleene Algebra With Top and Tests}}
{Principle Of Programming Language (POPL)}
{}{}

\cventry{2020}
{Mark Lemay, Cheng Zhang, William Blair}
{\href{https://icfp20.sigplan.org/details/tyde-2020-papers/7/Developing-a-Dependently-Typed-Language-with-Runtime-Proof-Search-Extended-Abstract-}
{Developing a Dependently Typed Language with Runtime Proof Search (Extended Abstract)}}
{Workshop on Type-Driven Development (TyDe)}
{}{}

\cventry{2018}
{Cheng Zhang}
{\href{http://hdl.handle.net/11040/24570}{King in Generalized Tournaments}}
{Wheaton College Honor Thesis}
{}{}

\cventry{2018}
{Cheng Zhang, Weiqi Feng, Emma Steffens, Alvaro de Landaluce, Scott Kleinman, Mark D. LeBlanc}
{\href{https://dl.acm.org/doi/10.5555/3205191.3205205}{Lexos 2017: Building Reliable Software in Python}}
{Journal of Computing Sciences in Colleges}
{}{}


\section{Research Talks}

\cventry{2018}
{Cheng Zhang, Mark D. LeBlanc}
{Lexos 2017: Building Reliable Software in Python}
{Conference for Computing in Small Colleges, UNH-Manchester}
{}{}

\cventry{2018}
{Cheng Zhang}
{Kings in Quasi-transitive Oriented Graph}
{Wheaton Summit For Woman In STEM}
{}{}


\section{Research Projects}

\cventry{2021 --- Now}
{Probabilistic Kleene Algebra}
{Boston University}{Boston, MA}{}
{Examine the mathematical foundation of probabilistic Kleene Algebra 
and its potential application in analysis of probabilistic programs.
This work will give rise to a unified approach to analysis probabilistic programs,
provide ways to prove program correctness, 
and identify the probability to encounter bugs in probabilistic programs.}

\cventry{2020 --- Now}
{Algebraic Formulation Of Incorrectness Logic}
{Boston University}{Boston, MA}{}
{Provide a algebraic formulation of Incorrectness Logic in TopKAT.
Our work leads to simpler proofs for program incorrectness, 
and demonstrates ways to automatically certify about bugs in programs.
We have also showed that TopKAT is a minimal framework to model incorrectness,
as it is impossible to encode incorrectness logic in KAT.
}

\cventry{2017 --- 2018}
{Mathematics Honor Thesis}
{Wheaton College} {Norton, MA}{}
{Studied kings in generalizations of tournament,
with a special focus on quasi-transitive oriented graphs.
I have shown that all the quasi-transitive oriented graphs
can be condensed into a tournament via tie component condensation, 
and tie component condensation of quasi-transitive 
oriented graphs is the most efficient condensation to tournament.
}

\cventry{2015 --- 2018}
{Software Lead}
{Lexomics Research Group, Wheaton College}
{Norton, MA}{}
{
  Led a group of undergraduate engineers through a major factorization of 
  the natrual language processing (NLP) software 
  \href{https://github.com/WheatonCS/Lexos}{Lexos}.
  In the process, I implemented modern software development workflows and
  transitioned the code base to a functional-first paradigm for ease of maintenance.
  I have also proposed a new architecture for side-effect management in Python.
}


\section{Honors And Fellowships}
\cvitem{2018 --- Now} {A member of Phi Beta Kappa Honor Society.}
\cvitem{2018}{Boston University Dean's Fellowship.}
\cvitem{2018}{Phi Beta Kappa Graduate Scholarship.}
\cvitem{2018} { Madeleine F. Clark Wallace Mathematics Prize.}
\cvitem{2018}{Fred Kollett Prize in Mathematics \& Computer Science.}
\cvitem{2017}{Weaton College Faculty-Student Research Awards.}
\cvitem{2016}{Wheaton Fellows.}
\cvitem{2014 --- 2018}{Wheaton College Dean's Lists.}
\cvitem{2014 --- 2018}{Wheaton College International Scholarship.}


\section{Skills}

\cvline{}{\textbf{Programming Languages}: Haskell, Ocaml, ATS, TypeScript, C\#, Java, C++}
\cvline{}{\textbf{Scripting Languages}: Python, Powershell, JavaScript}
\cvline{}{\textbf{Formal Methods}: Coq, Lean, MathComp Z3, EasyCrypt, Agda}
\cvline{}{\textbf{Data Processing}: Panda, Scikit-Learn, Numpy, R, Stata}
\cvitem{}{\textbf{Tools}: Git, \LaTeX, SSH}

\section{Experiences}

\cventry{2021 --- Now}
{Organizer}
{Principle of Programming and Verification Seminar}
{Boston University}{Boston, MA}
{Invite and communicate with seminar speakers;
organize all the seminar information on the webpage, mailing list, and calendar;
and host the speaker during the seminar.}

\cventry{2020 --- Now}
{Organizer}
{Programming Language Reading Group}
{Boston University}{Boston, MA}
{Assign the reading material every week,
organize and schedule the weekly meeting for the reading group,
and host the discussion on the reading material.}

\cventry{2019 --- Now}
{Graduate Researcher}
{Boston University}
{Boston, MA}{}
{Study various extensions of Kleene Algebra, and their use in program analysis.
My researches provide easier, even automated, proofs for program analysis.
}

\cventry{2019 --- 2021}
{Teaching Fellow}
{Boston University}
{Boston, MA}{}
{
  Taught Principle of Programming Language, Introduction to Computer Science,
  Algebra Algorithm, Geometric Algorithm, etc.
}

\cventry{2019}
{Grader}
{Boston University CS 511 Formal Method}
{Boston, MA}{}
{Provided solutions to homework problems, graded the homework,
organize useful statistics for the professor, 
and provided hints and answered questions piazza when necessary.}

\cventry{2017 --- 2018}
{Grader}
{Wheaton College MATH 241 Theory of Probability}
{Norton, MA}{}
{Graded homework, gave feedback to students on each individual homework,
and provide informative statistics to the professor on the homework.}

\end{document}
